---
title: "Manipal Prolearn"
output: 
  flexdashboard::flex_dashboard:
    #orientation: columns
    vertical_layout: fill
---

```{r }
library(flexdashboard)
library(stringr)
library(readxl)
library(dplyr)
library(DT)
library(ggplot2)
library(data.table)
library(plotly)
url <- "C:/Users/Administrator/Desktop/Data Visualisation/Data Set/DV- Case Study"
files <- list.files(url, pattern ="\\.xlsx")
revenue <- data.frame()
lead<- data.frame()
for(i in files){
  temp <- data.frame() 
  if (str_detect(i, "2017_Revenue") == TRUE){
    temp <- read_excel(paste(url,i, sep = "/"))
    revenue <- rbind(revenue, temp)
    }
  else{
    temp <- read_excel(paste(url,i, sep = "/"))
    lead <- rbind(lead, temp)}
}
```

Problem 1:{data-orientation=Column data-navmenu="Problems"}
===========================
Column {data-width=350}
-----------------------------------------------------------------------

### Data of Sources Providing Leads

```{r}
source_lead_enroll <- read.csv("C:/Users/Administrator/Desktop/Data Visualisation/Data Set/DV- Case Study/Source_wise_lead.csv", stringsAsFactors = FALSE)
source_lead_enroll <- source_lead_enroll %>%  filter(Admission != "#N/A")
datatable(source_lead_enroll, options = list(pageLength = 10))

```

Column {.tabset data-width=650}
-----------------------------------------------------------------------

### Chart A

```{r}
best_10 <- source_lead_enroll %>% arrange(-Admission) %>% head(10)
p1 <- ggplot(best_10, aes(x= reorder(Source.Bucket,Admission) , y = Admission, fill = Source.Bucket)) + geom_bar(stat = "identity") +  theme_bw() +
  ggtitle("Source Lead as per Count of Admission") + theme(axis.text.x = element_blank(), axis.title.y = element_blank(), axis.title.x = element_blank()) +theme(legend.position = "bottom")
ggplotly(p1)
```

### Chart B

```{r}
best10 <- source_lead_enroll %>% arrange(-Coversion_Rate) %>% head(10)
p2 <- ggplot(best10, aes(x= reorder(Source.Bucket,Coversion_Rate), y = Coversion_Rate, fill = Source.Bucket)) + geom_bar(stat = "identity") +theme_bw() +
  ggtitle("Source Lead Conversion Percentage") +theme(axis.text.x = element_blank(), axis.title.y = element_blank(), axis.title.x = element_blank()) +theme(legend.position = "bottom")
ggplotly(p2)
```
 
Problem 2 {data-orientation=rows data-navmenu="Problems"}
==============================================

Row {data-width=250}
-------------------------------------------------------
### Best Course 
```{r}
unique_leads <- unique(setDT(revenue), by = c("Order Email"))
best_product <- unique_leads%>% group_by(`Course Title`) %>% summarise(Count = n()) %>%  arrange(-Count) %>% head(1)
a <- best_product$`Course Title`
valueBox(a, icon = "fa-book", color = "Green")
```

### Total Admission
```{r}
best_product <- revenue %>% group_by(`Course Title`) %>% summarise(Count = n()) %>%  arrange(-Count) %>% head(1)
a <- best_product$Count
valueBox(a, icon = "fa-graduation-cap", color = "Blue")
```

### Total Revenue
```{r}
total <- revenue %>% group_by(`Course Title`) %>% summarise(Total = sum(`Order Total`)) %>%  arrange(-Total) %>% head(1)
b <- total$Total
valueBox(b, icon = "fa-rupee", color = "Red")
```

Row {.tabset}
-----------------------------------------------------

### Focus Areas
```{r}
revenue_new <- revenue %>%  group_by(`Course Title`) %>% summarise(Revenue = sum(`Order Total`)) %>% arrange(-Revenue)
q1 <- quantile(revenue_new$Revenue, probs = .25)
q2 <- quantile(revenue_new$Revenue, probs = .50)
q3 <- quantile(revenue_new$Revenue, probs = .75)
revenue_new$Status <- ifelse(revenue_new$Revenue < q1,"Poor",
                             ifelse(revenue_new$Revenue <q2, "Need Improvement",
                                    ifelse(revenue_new$Revenue <q3, "Good", "Excellent")))
datatable(revenue_new, options = list(pageLength = 10))

```

### Low Perfomance 
```{r}
poor <- subset(revenue_new, revenue_new$Status=="Poor")
poor_new <- poor %>% arrange(Revenue) %>%  head(10)

plot_ly(poor_new, x= ~reorder(`Course Title`,-Revenue),y = ~Revenue,color = ~`Course Title`, type = "bar", text = ~Revenue, textposition = 'auto',
             marker = list(color = 'rgb(158,202,225)',
                line = list(color = 'rgb(8,48,107)', width = 1.5))) %>% layout(title = "Poor Performing Products", xaxis = list(title = ""),yaxis = list(title = ""))
```

###Need Improvement 
```{r}
m1 <- subset(revenue_new, revenue_new$Status=="Need Improvement")
m1_new <- m1 %>% arrange(Revenue) %>%  head(10)

plot_ly(m1_new, x= ~reorder(`Course Title`,-Revenue),y = ~Revenue, type = "bar",color = ~`Course Title`, text = ~Revenue, textposition = 'auto',
             marker = list(color = 'rgb(158,202,225)',
                line = list(color = 'rgb(8,48,107)', width = 1.5))) %>% layout(title = "Products That Need Improvement", xaxis = list(title = ""),yaxis = list(title = ""))
```


### Good Performance
```{r}
m2 <- subset(revenue_new, revenue_new$Status=="Good")
m2_new <- m2 %>% arrange(Revenue) %>%  head(10)

plot_ly(m2_new, x= ~reorder(`Course Title`,-Revenue),y = ~Revenue, type = "bar", text = ~Revenue, textposition = 'auto',
             marker = list(color = 'rgb(158,202,225)',
                line = list(color = 'rgb(8,48,107)', width = 1.5))) %>% layout(title = "Products Performing above Average", xaxis = list(title = ""),yaxis = list(title = ""))
```


### Exceptional Performance 
```{r}
excellent <- subset(revenue_new, revenue_new$Status=="Excellent")
excellent_new <- excellent %>%  head(10)

plot_ly(excellent_new, x= ~reorder(`Course Title`,-Revenue),y = ~Revenue, type = "bar", text = ~Revenue, textposition = 'auto',marker = list(color = 'rgb(158,202,225)',
                line = list(color = 'rgb(8,48,107)', width = 1.5))) %>% layout(title = "Products Performing Excellent", xaxis = list(title = ""),yaxis = list(title = ""))
```


Problem 3 {data-orientation=columns data-navmenu="Problems"}
======================================================

Column {data-width=350}
------------------------------------------------------

#### Data
```{r}
total_calls_assinged <- na.omit(lead %>% group_by(`Assigned To`) %>% summarise(total_calls_made=n()) %>% arrange(-total_calls_made))

total_success_assinged<- na.omit(lead %>% group_by(`Assigned To`,Status) %>% filter(Status=="Interested/Follow Up") %>% summarise(total_responce=n()) %>% arrange(-total_responce))

total_success_rate_assinged <- merge(total_success_assinged,total_calls_assinged) %>%  mutate(success_rate=round(total_responce*100/total_calls_made,2)) %>% arrange(-success_rate) %>% head(10)

datatable(total_success_rate_assinged, options = list(pageLength = 10))

```

Column{data-width=650}
-----------------------------------------------------

### Couseller Vs Success Rate 
```{r}
plotly_success_rate= total_success_rate_assinged %>% arrange(-success_rate) %>% plot_ly(x= ~reorder(`Assigned To`,-success_rate), y=~success_rate, text = ~success_rate, textposition = 'auto',marker = list(color = 'rgb(158,202,225)',
                line = list(color = 'rgb(8,48,107)'))) %>%   layout(xaxis = list(title="Counselor"), yaxis =list(title="Success Rate") )

plotly_success_rate
```

Problem3 (Cont.) {data-navmenu="Problems"}
=====================================================

### Chart As A Heat Map
````{r}
total_admission_by_counseler_coursewise <- revenue %>% filter(`Payment Status`=="success") %>% group_by(`Counselor Name`,`Course Title`) %>% summarise(Total_revenue_generated=sum(Amount),success_transaction=n())
#,`Course Title`%in% c(pgd,pt,adv)


total_success_assinged_coursewise<- na.omit(lead %>% group_by(`Assigned To`,Course,Status) %>% filter(Status=="Interested/Follow Up")  %>% summarise(tot_responce=n()) %>% arrange(`Assigned To`))

total_calls_assinged_coursewise <- na.omit(lead %>% group_by(`Assigned To`,Course) %>% summarise(total_calls_made=n()) %>% arrange(-total_calls_made))

total_success_rate_assinged_coursewise <- merge(total_success_assinged_coursewise,total_calls_assinged_coursewise,by=c("Assigned To","Course")) %>%  mutate(success_rate=tot_responce*100/total_calls_made) %>% arrange(Course,-success_rate)  
df <- total_success_rate_assinged_coursewise[,c(1,2,6)]

#In ggplot

# success_rate_bar_coursewise<- total_success_rate_assinged_coursewise %>% arrange(-success_rate) %>% ggplot(aes(x=reorder(`Assigned To`,-success_rate),y=Course,fill=-success_rate,text=paste("success/call:",paste(tot_responce,total_calls_made,sep = "/"))))+geom_tile()+theme_bw()+ labs(x="Counselor",y="")+
#   theme(axis.text.x = element_text(angle = -45,hjust = 0))+labs(x="Assigned to",y="Course",title="Courseswise success rate for Counselors")
# 
# 
# ggplotly(success_rate_bar_coursewise,tooltip = c("x","y","text","fill"))

success_rate_bar_coursewise<- total_success_rate_assinged_coursewise %>% arrange(-success_rate) %>% ggplot(aes(x=reorder(`Assigned To`,-success_rate),y=Course,fill=-success_rate,text=paste("success/call:",paste(tot_responce,total_calls_made,sep = "/"))))+geom_tile()+theme_bw()+ labs(x="Counselor",y="")+
  theme(axis.text.x = element_text(angle = -90,hjust = 0))+labs(x="Assigned to",y="Course",title="Courseswise success rate for Counselors")

ggplotly(success_rate_bar_coursewise,tooltip = c("x","y","text","fill"))

```


Problem 4 {data-orientation=columns data-navmenu="Problems"}
======================================================

Column {data-width=450}
------------------------------------------------------

#### OverAll Data
```{r}
#==================== APRIL ==================#

april <- read_excel("April Leads.xlsx")


april_rev <- read_excel("April 2017_Revenue sheet.xlsx", sheet = 1)

# April Revenue
april_rev_new <- april_rev[complete.cases(april_rev$Location),]

april_rev_new <- april_rev_new %>% select(`Order Email`,Location,`Student Name`,`Mobile Number`,`Course Title`)


april_rev_new$`Order Email` <- as.character(april_rev_new$`Order Email`)
april_rev_new$Location <- as.character(april_rev_new$Location)
april_rev_new$`Student Name` <- as.character(april_rev_new$`Student Name`)
april_rev_new$`Mobile Number` <- as.numeric(as.character(april_rev_new$`Mobile Number`))
april_rev_new$`Course Title` <- as.character(april_rev_new$`Course Title`)


april_rev_new$Location <- toupper(april_rev_new$Location)

april_rev_count <- april_rev_new %>% group_by(Location) %>% summarise(Count = n()) %>% as.data.frame()
april_rev_count$Month <- "April"

# April Lead
april_lead <- april %>% select(City,Name,Email,Course,Status)

april_lead_new <- april_lead[complete.cases(april_lead$City),]


april_lead_new$City <- toupper(april_lead_new$City)

april_lead_count <- april_lead_new %>% 
  filter(Status %in% c("Call Back","Interested/Follow Up","Admission Taken")) %>% 
  group_by(City,Status) %>% summarise(Count = n()) %>% as.data.frame()
april_lead_count2 <- april_lead_count[which(april_lead_count$City %in% april_rev_count$Location),]

april_lead_count2$Month <- "April"


#=========================== MARCH ====================#

march <- read_excel("March Leads.xlsx")

march_rev <- read_excel("March 2017_Revenue sheet.xlsx", sheet = 1)

# March Revenue
march_rev_new <- march_rev[complete.cases(march_rev$Location),]
march_rev_new <- march_rev %>% select(`Order Email`,Location,`Student Name`,`Mobile Number`,`Course Title`)

march_rev_new$`Order Email` <- as.character(march_rev_new$`Order Email`)
march_rev_new$Location <- as.character(march_rev_new$Location)
march_rev_new$`Student Name` <- as.character(march_rev_new$`Student Name`)
march_rev_new$`Mobile Number` <- as.numeric(as.character(march_rev_new$`Mobile Number`))
march_rev_new$`Course Title` <- as.character(march_rev_new$`Course Title`)

march_rev_new$Location <- toupper(march_rev_new$Location)

march_rev_count <- march_rev_new %>% group_by(Location) %>% summarise(Count = n()) %>% as.data.frame()
march_rev_count <- march_rev_count[1:(nrow(march_rev_count)-1),]

march_rev_count$Month <- "March"
# March Lead
march_lead <- march %>% select(City,Name,Email,Course,Status)


march_lead_new <- march_lead[complete.cases(march_lead$City),]

march_lead_new$City <- toupper(march_lead_new$City)

march_lead_count <- march_lead_new %>% 
  filter(Status %in% c("Call Back","Interested/Follow Up","Admission Taken")) %>%
  group_by(City,Status) %>% summarise(Count = n()) %>% as.data.frame()
march_lead_count2 <- march_lead_count[which(march_lead_count$City %in% march_rev_count$Location),]
march_lead_count2$Month <- "March"

#======================== MAY ==========================#
may <- read_excel("May leads.xlsx")

may_rev <- read_excel("May 2017_Revenue sheet.xlsx", sheet = 1)

# May Revenue
may_rev_new <- may_rev[complete.cases(may_rev$Location),]
may_rev_new <- may_rev %>% select(`Order Email`,Location,`Student Name`,`Mobile Number`,`Course Title`)

may_rev_new$`Order Email` <- as.character(may_rev_new$`Order Email`)
may_rev_new$Location <- as.character(may_rev_new$Location)
may_rev_new$`Student Name` <- as.character(may_rev_new$`Student Name`)
may_rev_new$`Mobile Number` <- as.numeric(as.character(may_rev_new$`Mobile Number`))
may_rev_new$`Course Title` <- as.character(may_rev_new$`Course Title`)

may_rev_new$Location <- toupper(may_rev_new$Location)

may_rev_count <- may_rev_new %>% group_by(Location) %>% summarise(Count = n()) %>% as.data.frame()
may_rev_count <- may_rev_count[1:(nrow(may_rev_count)-1),]
may_rev_count$Month <- "May"

# May Lead
may_lead <- may %>% select(City,Name,Email,Course,Status)


may_lead_new <- may_lead[complete.cases(may_lead$City),]

may_lead_new$City <- toupper(may_lead_new$City)

may_lead_count <- may_lead_new %>% 
  filter(Status %in% c("Call Back","Interested/Follow Up","Admission Taken")) %>%
  group_by(City,Status) %>% summarise(Count = n()) %>% as.data.frame()
may_lead_count2 <- may_lead_count[which(may_lead_count$City %in% may_rev_count$Location),]

may_lead_count2$Month <- "May"

#====================COMBINE FILES===================#

revenue <- rbind(march_rev_count,april_rev_count,may_rev_count)
lead <- rbind(march_lead_count2,april_lead_count2,may_lead_count2)

rownames(revenue) <- 1:nrow(revenue)
rownames(lead) <- 1:nrow(lead)

lead_overall <- lead %>% group_by(City,Month) %>% summarise(Overall = sum(Count))
lead_overall$Type = "Lead"
lead_overall <- as.data.frame(lead_overall)

newdf <- data.frame(City = revenue$Location, Month = revenue$Month, Overall = revenue$Count)
newdf$Type = "Revenue"
newdf$City <- as.character(newdf$City)
newdf$Month <- as.character(newdf$Month)

newdf <- rbind(newdf, lead_overall)
datatable(newdf, options = list(pageLength = 10))
```

Column {.tabset}
---------------------------------

### Chart A
```{r}
#====================PLOT=======================#
plot_ly(revenue, x = ~Location, y = ~Count, frame = ~Month,
        type = "bar", text = ~Count, marker = list(color = 'rgb(8,48,107)')) %>% 
  layout(title = "Students joined wrt to location",
         xaxis = list(title = ""),
         yaxis = list(title = ""))

```


### Chart B
```{r}
plot_ly(lead, x = ~City, y = ~Count, frame = ~Month,
        type = "bar", name = ~Status) %>% 
  layout(barmode = "stack",
         title = "No of students who were interested")
```


### Chart C
```{r}
plot_ly(newdf, x = ~City, y = ~Overall, frame = ~Month, type = "bar", name = ~Type) %>% 
  layout(barmode = "group")

```

```{r}

```